---
title: "assign4"
output: html_notebook
---


For the regular expression exercises, try writing first using regular expressions directly, then try using rverbalexpressions. Provide the code for both. 

```{r libraries}
library(lubridate)
library(stringr)
library(RVerbalExpressions)

```


# Part 1

## R4DS 16.4.5

**Create a vector of dates giving the first day of every month in the current year. **
```{r generate year}
ymd_v <- ymd(str_c(year(now()), ",", seq(1, 12, 1), ",01"))
ymd_v
```


**Write a function that given your birthday (as a date), returns how old you are in years.**

```{r calculate age}
count_age <- function(x){
  age <- year(now())-year(ymd(x))
  age
}
count_age(19960406)
```


**Write a function that given your birthday, returns the day of the week you were born on. **

```{r calculate weekday}
call_week <- function(x){
  weekday <- wday(ymd(x),label = T)
  weekday
}
call_week(19960406)
```


## R4DS 14.3.2.1

**Given the corpus of common words in stringr::words, create regular expressions that find all words that have seven letters or more. (Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.)**

```{r import data, include=FALSE}
stringr::words
```

```{r more than 7}
str_view(words, "\\w{7,}", match = TRUE)
```


## R4DS 14.3.3.1

**Use str_detect to find all words that:**

**That only contain consonants. (Hint: thinking about matching “not”-vowels.)**

```{r only consonants}
str_view(words, "^[^aeiou]+$", match = TRUE)
```

**Empirically verify the rule “i before e except after c”.**

```{r no c before ie}
str_view(words, "[^c]ie", match = TRUE)
```

**Create a regular expression that will match telephone numbers as commonly written in the US. Split this up into multiple expressions as needed.**

```{r telephone number}
telen <- rx() %>%
  rx_start_of_line() %>%
  rx_digit() %>%
  rx_repeat_previous(3) %>%
  rx_any_of(".-") %>%
  rx_digit() %>%
  rx_repeat_previous(3) %>%
  rx_any_of(".-") %>%
  rx_digit() %>%
  rx_repeat_previous(4) %>%
  rx_end_of_line() 
telen
```


# Part 2


Choose a dataset (this can be the same dataset as the last assignment, or a new one). Define a predictive modeling problem. Create the appropriate files and notebooks to do the following:

1. Describe the data and the problem

2. Read in and check data

2. Clean up the data. 

*Note: You may request that score for these sections replace your score for the coding portion of Assignment 3.*

4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended. 

5. Prepare the data for modeling

Note: this will form the basis for your midterm project. Take advantage of TA's and my office hours. We can provide feedback and guidance. 

